
\section{Introduction}


Welcome to Bertini\_real, software for real algebraic geometry.  This manual is intended to help the user operate this piece of numerical software, to obtain useful and high-quality results from decomposing real algebraic curves and surfaces.

Bertini\_real is compiled software, links against a parallel version of Bertini 1 compiled as a library ({\tt libbertini-parallel}, and requires Matlab and the Symbolic Computation toolbox.  It also requires several other libraries, including a few from Boost, and an installation of MPI.  All libraries should be compiled using the same compilers and dependent libraries.  



\subsection{About this manual}
The purpose of this manual is to provide a robust, orderly, and easy to understand instructions on how to use Bertini\_real. This manual has three roles: it first serves as a description of what Bertini\_real is, followed by instructions on Bertini\_real's installation on Mac, Linux, and PC operating systems, and finally as a general reference manual for Bertini\_real.
	
This manual is here to help guide a user through the installation process, as well as act as the user's manual for Bertini\_real. If there is a section that might not be entirely clear, or is confusing to a reader, please contact us (see below for contact information), and we will try to resolve the problem. Such feedback is welcome!


\subsection{Bertini\_real product description}
	Bertini\_real is an implementation of several numerical algorithms \cite{lu2007finding,besana2013cell}, to decompose the real part of a complex curve or surface in any (tractible) number of variables.
	Some of the important features of Bertini\_real include :
\begin{itemize}
\item It is a command line program for numerically decomposing the real portion of a one- or two- dimensional complex irreducible algebraic  set in any reasonable number of variables.
\item It seeks to automate the visualization and computation of algebraic curves and surface.
\end{itemize}



\subsection{Where Bertini\_real can be found}
		
	The code for Bertini\_real can be found at \href{https://github.com/ofloveandhate/bertini_real}{GitHub}.  Take a recursive clone to pick up submodules.  You have to build it from source yourself; pre-compiled binaries are not offered. 


	\subsection{Who is developing Bertini\_real?}

	Bertini\_real is under ongoing development by the development team, which consists of 

	\begin{itemize}
		\item silviana amethyst (University of Wisconsin - Eau Claire, main implementer)  \\ \href{mailto:silviana.amethyst@gmail.com}{silviana.amethyst@gmail.com} 
		\item Dan Bates (US Naval Academy, Advisor)
		\item Jonathan Hauenstein (University of Notre Dame, Advisor)
		\item Wenrui Hao (Penn State, Non-self-conjugate case)
		\item Andrew Sommese (University of Notre Dame, Advisor)
		\item Charles Wampler (General Motors. R\&D, Advisor)
		\item Pierce Cunneen (University of Notre Dame, Windows use) 
		\item Nicolle Ho (Notre Dame, Python curve visualization)
		\item Elizabeth Sudkamp (Notre Dame, Windows use, symbolics in Python)
	\end{itemize}
	This manual was written by silviana amethyst, Pierce Cunneen, Chris Lembo, and Elizabeth Sudkamp.

% FUTURE CONTRIBUTORS, please add your name.


\subsection{Acknowledgements}

The development of Bertini\_real has been supported generously by a number of sources, including 
\begin{itemize}[noitemsep]
\item the Vincent J. and Annamarie Duncan Professor of Mathematics, at the University of Notre Dame, 
\item the University of Notre Dame, 
\item the National Science Foundation grants DMS-1025564 , DMS-1115668, and DMS-1262428, 
\item the Air Force Office of Scientific Research grant FA8650-13-1-7317, 
\item Mathematical Biosciences Institute, 
\item the Sloan Research Fellowship, 
\item the Army Young Investigators Project, and 
\item the Defense Advanced Research Projects Agency Young Faculty Award.
\end{itemize}

Finally, funding for shared facilities used in this research was provided by the Division of Computer and Network Systems: an NSF grant under award number CNS-0923386.




\subsection*{Disclaimer}

Any opinions, findings, and conclusions or recommendations expressed in this material are those of the author(s) and do not necessarily reflect the views of the National Science Foundation or any other organization.
